Test SUSIE for regions near genes (500kb flanking)

### 2020-06-25 analysis/index.Rmd
SUSIE examples

  * [Using UKbiobank data (chr22), fusion weights Adipose, `L=1`](simulation-susie-ukbchr22-gtex.adipose.html)

>>>>

  * [Using UKbiobank data (chr22), fusion weights Adipose, `L=1`](simulation-susie-ukbchr22-gtex.adipose.html)
  * [Using UKbiobank data (chr22), fusion weights Adipose, `L=2`](simulation-susie-ukbchr22-gtex.adipose-L=2.html)
   * [Using UKbiobank data (chr22), fusion weights Adipose, `L=3`](simulation-susie-ukbchr22-gtex.adipose-L=3.html)

### 2020-06-25 analysis/simulation-susie-ukbchr22-gtex.adipose-L=2.Rmd
SUSIE examples

### SUSIE results: PIP > 0.3 or causal genes

```{r sim 5, include= F, echo = F, eval = F, warning= F}
# displaying not right
resall <- Sys.glob(paste0(outputdir, tag, ".", tag2, "*-susieres.txt"))
l <- htmltools::tagList()
res <- resall[1]
for (i in 1:8){
  res <- resall[i]
  name <- gsub(".*res-(.+)-susie.*", "\\1", res)
  l[[i]] <- plot_all(res, mrashres.gene, mrashres.snp, name)
}
l
```

```{r sim 5 examples,  out.width = "98%", out.height="95%", warning= F}
# displaying not right
res <- paste0(outputdir, tag, ".", tag2, "-LL22NC03-86G7.1-susieres.txt")
name <- gsub(".*res-(.+)-susie.*", "\\1", res)
plot_all(res, mrashres.gene, mrashres.snp, name)
```

>>>>

### SUSIE results

```{r sim 5, include= F, echo = F, eval = F, warning= F}
# displaying not right
resall <- Sys.glob(paste0(outputdir, tag, ".", tag2, ".L2*-susieres.txt"))
l <- htmltools::tagList()
res <- resall[1]
for (i in 1:8){
  res <- resall[i]
  name <- gsub(".*res-(.+)-susie.*", "\\1", res)
  l[[i]] <- plot_all(res, mrashres.gene, mrashres.snp, name)
}
l
```

```{r sim 5 examples,  out.width = "98%", out.height="95%", warning= F}
# displaying not right
res <- paste0(outputdir, tag, ".", tag2, ".L2-LL22NC03-86G7.1-susieres.txt")
name <- gsub(".*.L2-(.+)-susie.*", "\\1", res)
plot_all(res, mrashres.gene, mrashres.snp, name)
```

### 2020-06-25 analysis/simulation-susie-ukbchr22-gtex.adipose-L=3.Rmd
SUSIE examples

```{r sim 5, include= F, echo = F, eval = F, warning= F}
# displaying not right
resall <- Sys.glob(paste0(outputdir, tag, ".", tag2, ".L2*-susieres.txt"))
l <- htmltools::tagList()
res <- resall[1]
for (i in 1:8){
  res <- resall[i]
  name <- gsub(".*res-(.+)-susie.*", "\\1", res)
  l[[i]] <- plot_all(res, mrashres.gene, mrashres.snp, name)
}
l
```

```{r sim 5 examples,  out.width = "98%", out.height="95%", warning= F}
# displaying not right
res <- paste0(outputdir, tag, ".", tag2, ".L2-LL22NC03-86G7.1-susieres.txt")
name <- gsub(".*.L2-(.+)-susie.*", "\\1", res)
plot_all(res, mrashres.gene, mrashres.snp, name)
```

>>>>

```{r sim 5, include= F, echo = F, eval = F, warning= F}
# displaying not right
resall <- Sys.glob(paste0(outputdir, tag, ".", tag2, ".L3*-susieres.txt"))
l <- htmltools::tagList()
res <- resall[1]
for (i in 1:8){
  res <- resall[i]
  name <- gsub(".*res-(.+)-susie.*", "\\1", res)
  l[[i]] <- plot_all(res, mrashres.gene, mrashres.snp, name)
}
l
```

```{r sim 5 examples,  out.width = "98%", out.height="95%", warning= F}
# displaying not right
res <- paste0(outputdir, tag, ".", tag2, ".L3-LL22NC03-86G7.1-susieres.txt")
name <- gsub(".*.L3-(.+)-susie.*", "\\1", res)
plot_all(res, mrashres.gene, mrashres.snp, name)
```
